A Software Engineering Perspective on \\ OpenMP and PThreads

### 2017-10-16 sections/04-research-design.tex
Improve pseudocode.

>>>>

\begin{figure}[htb]
\begin{minipage}{\linewidth}
\begin{lstlisting}[language=C, basicstyle=\ttfamily\scriptsize, numbers=left,
                   frame=no, showspaces=false, showstringspaces=false,
                   numberstyle=\tiny,
                   xleftmargin=0.5cm,
                   keywords={%
                       DATATYPE, pthread_t, pthread_create,
                       pthread_join, task_function, NULL, int, main,
                       void, printf, return, pthread_mutex_t,
                       pthread_attr_t, pthread_attr_init,
                       MAX_THREADS, SIZE, char, struct, malloc,
                       MIN, pthread_mutex_lock, pthread_mutex_unlock,
                       pthread_exit, from, to, and%
                       },
                   otherkeywords={::, \#pragma, \#include, <<<,>>>, \&, \*, +, -, /, [, ], >, <}
                   ]
z = 0;
for(x from 0 to x_max - 1) {
    /* Independent iterations */
    for(y from 0 to y_max - 1) {
        /* Independent iterations */
        for (iteration from 0 to iteration_max,
             and f_c(z) < limit) {
            /* Iterations depend on
               previous values of z */
            z = f_c(z);
        }
    }
}
\end{lstlisting}
\end{minipage}
\caption{Pseudocode for the computation of the Mandelbrot set}
\label{lst:mandelbrot-pseudo}
\end{figure}

The Mandelbrot set is informally defined as the set of complex numbers $c$ for
which the function $f_c(z) = z^2 + x$ does not diverge when iterated starting
in $z=0$, that is, the sequence the sequence $f_c(0), f_c(f_c(0)),
f_c(f_c(f_c(0))),\dots$ is always limited. Figure~\ref{lst:mandelbrot-pseudo}
shows pseudocode for the computation of the Mandelbrot set, listing which loops
have dependent and independent iterations.
